---
title: "Capstone Project Proposal"
author: "Samata"
date: "September 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This document contains my proposal for a Capstone Project that I will be completing. I have decided to use the data that IBM has created of employee attrition which includes information including their salary, gender, travel, job satisfaction, year of service etc.  
I will be using data to answer some of the common questions including but not limited to  
  1) Common character of those lost in  attrition?  
  2) Is there a relation between monthly income and attrition?  
  3) What's the common characteristics among those with no attrition?  
  
The purpose of the project is to answer the above questions such that the client knows  true reason behind employee attrition and the necessary steps it needs to take.  

Data received has about 35 columns. Below it shows all the column that the data provide.   I don't believe that all the columns are equally vital for the analysis.  I will be using the information that I think are necessary for the client to make a decision.

```{r}
#Create Directory
setwd("C:/Users/pankaj/Desktop/Samata/Springboard/Project/")
#Import File
Employee_Attrition <- read.csv(file.choose(), header=TRUE)
attach(Employee_Attrition)

head(Employee_Attrition, n=0)
```


